\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators

### 2023-02-16 Manuscript/Trial.Rmd
brief descrp of repro traits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=12, fig.width=18, out.width="80%",fig.align='center',fig.cap= "\\textbf{Figure 2.} Location of the different qualitative traits in the trait space. The figure panel is composed of the traits that showed statistical association with the first two axes of trait variation: compatibility system (a), life form (b), lifespan (c), breeding system (d), flower shape (e) and flower symmetry (f). The solid arrows indicate the direction of variation of the different quantitative traits shown in figure 1: flower number (FN), plant height (PH), style length (SL), flower size (FS), ovule number (ON) and the level of autonomous selfing (S)."}

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
library(ggstar)

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.6)),
            axis.text=element_text(size = rel(1.6), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(size = rel(1.1)),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank(),
            plot.title = element_text(size = rel(2.5), face="bold")
      ))
}

#Load data
dat_cleaning_5 <- readRDS("../Data/RData/data_all_species_for_rmd_plot_ppca_QUALITATIVE.rds")
phyl_pca_forest <- readRDS("../Data/RData/phyl_pca_forest.rds")

#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
Compatibility <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Compatibility <- dat_cleaning_5$Compatibility_system
  dat$Compatibility <- as.character(dat$Compatibility)
  dat$Compatibility[dat$Compatibility=="dioecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="monoecious"] <- "Unisexual flowers"
  dat$Compatibility[dat$Compatibility=="partially_self_compatible"] <- "Partially self compatible"
  dat$Compatibility[dat$Compatibility=="self_compatible"] <- "Self compatible"
  dat$Compatibility[dat$Compatibility=="self_incompatible"] <- "Self incompatible"
  dat$Compatibility <- factor(dat$Compatibility, levels = c("Self compatible", "Partially self compatible", "Self incompatible", "Unisexual flowers"))

  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Compatibility, fill=Compatibility), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("deepskyblue2", "purple2","goldenrod","gray7")) +
scale_starshape_manual(values = c(13, 15, 28, 5))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("(a)") + xlab(NULL)  + ylab("Autonomous selfing - Floral display axis")

  plot

}

#Compatibility(PC)

#############################################################################################################################################################
#Life form
#############################################################################################################################################################
#Load plots
Life_form <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Life form` <- dat_cleaning_5$life_form
  dat$`Life form` <- as.character(dat$`Life form`)
  dat$`Life form`[dat$`Life form`=="herb"] <- "Herb"
  dat$`Life form`[dat$`Life form`=="shrub"] <- "Shrub"
  dat$`Life form`[dat$`Life form`=="tree"] <- "Tree"
  dat$`Life form`[dat$`Life form`=="vine"] <- "Shrub"

  dat$`Life form` <- factor( dat$`Life form`, levels = c("Herb", "Shrub", "Tree"))

plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Life form`, fill=`Life form`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("forestgreen", "darkorange2","black")) +
scale_starshape_manual(values = c(13, 15, 28))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.090, 0.115)) + ggtitle("(b)") +
    xlab(NULL) + ylab(NULL)

  plot

}

#Life_form(PC)

#############################################################################################################################################################
#Life span
#############################################################################################################################################################
#Load plots
Life_span <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
    dat$Lifespan <- dat_cleaning_5$lifespan
    dat$Lifespan <- as.character(dat$Lifespan)

  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=Lifespan, fill=Lifespan), size=2.25, color= NA, alpha = 0.9)+ scale_fill_manual(values=c("sienna4","forestgreen")) +
scale_starshape_manual(values = c(13, 15))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME
  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.12, 0.1)) + ggtitle("(c)") +
    xlab(NULL) + ylab(NULL)

  plot

}

#Life_span(PC)

#############################################################################################################################################################
#Flower symmetry
#############################################################################################################################################################
#Load plots
Flower_sym <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower symmetry` <- dat_cleaning_5$Flower_symmetry
  dat$`Flower symmetry` <- as.character(dat$`Flower symmetry`)
  dat$`Flower symmetry`[dat$`Flower symmetry`=="actinomorphic"] <- "Actinomorphic"
  dat$`Flower symmetry`[dat$`Flower symmetry`=="zygomorphic"] <- "Zygomorphic"

  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower symmetry`, fill=`Flower symmetry`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("goldenrod","purple2")) +
scale_starshape_manual(values = c(13, 15))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.1)) + ggtitle("(f)") + ylab(NULL) + xlab("Flower number - Flower size axis")

  plot

}

#Flower_sym(PC)

#############################################################################################################################################################
#Flower shape
#############################################################################################################################################################
#Load plots
Flower_sha <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Flower shape` <- dat_cleaning_5$Flower_morphology
  dat$`Flower shape` <- as.character(dat$`Flower shape`)
  dat$`Flower shape`[dat$`Flower shape`=="Funnelform"] <- "Campanulate"
  dat$`Flower shape`[dat$`Flower shape`=="Spike"] <- "Brush"

  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Flower shape`, fill=`Flower shape`), size=2.25, color= NA, alpha = 0.85)+ scale_fill_manual(values=c("black","goldenrod", "deepskyblue2","forestgreen","purple2","darkorange2")) +
scale_starshape_manual(values = c(13, 15, 28, 5, 9, 14))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME

  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.155, 0.17)) + ggtitle("(e)") + ylab(NULL) + xlab("Flower number - Flower size axis")

  plot

}

#Flower_sha(PC)

#############################################################################################################################################################
#Breeding system
#############################################################################################################################################################
#Load plots
Breeding_syst <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  #######
  #DENSITY FUNCTION
  #######
  get_density <- function(x, y, ...) {
    dens <- MASS::kde2d(x, y, ...)
    ix <- findInterval(x, dens$x)
    iy <- findInterval(y, dens$y)
    ii <- cbind(ix, iy)
    return(dens$z[ii])
  }

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$`Breeding system` <- dat_cleaning_5$Breeding_system
  dat$`Breeding system` <- as.character(dat$`Breeding system`)
  dat$`Breeding system` <- factor(dat$`Breeding system`, levels=c("Hermaphrodite","Monoecious" ,"Dioecious"))

  plot <- plot + geom_star(data=dat, aes(-x, -y, starshape=`Breeding system`, fill=`Breeding system`), size=2.25, color= NA, alpha = 0.9) + scale_fill_manual(values=c("forestgreen","darkorange2", "black")) +
scale_starshape_manual(values = c(13, 15, 28))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.2, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #Add axis with perctentage
  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.8, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

  #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.2,5.25,7.9,7.1,6)), y = -(PCAloadings$PC2*c(4.45,4.2,5.4,7.7,6,6.5)+c(0,0,0,0,-0.1,0)),
                          label = PCAloadings$Variables, color="black",size=6, fontface=2)

  #CHANGE THEME
  #CHANGE THEME

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.152, 0.11)) + ggtitle("(d)") +
    xlab("Flower number - Flower size axis") +
    ylab("Autonomous selfing - Floral display axis")

  plot

}

#Breeding_syst(PC)

#############################################################################################################################################################
#Nectar
#############################################################################################################################################################
#Load plots
#Nectar <- function(PC, x="PC1", y="PC2") {
#  # PC being a prcomp object
#  data <- data.frame(PC$S)
#  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
#  dat <- data.frame(x = data[,x], y = data[,y])
#  
#  #######
#  #DENSITY FUNCTION
#  #######
#  get_density <- function(x, y, ...) {
#    dens <- MASS::kde2d(x, y, ...)
#    ix <- findInterval(x, dens$x)
#    iy <- findInterval(y, dens$y)
#    ii <- cbind(ix, iy)
#    return(dens$z[ii])
#  }
#  
#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
#  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
#  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
#  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
#  dat$Nectar[dat$Nectar=="no"] <- "Absence"
#  plot <- plot + geom_point(data=dat, aes(-x, -y, #colour=Nectar),size=1.75)+scale_color_manual(values=c("black","grey"))
#  
#  ########
#  #ADD ARROWS 
#  ########
#  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
#  mult <- min(
#    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
#    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
#  )
#  datapc <- transform(datapc,
#                      v1 = .75 * mult * (get(x)),
#                      v2 = .75 * mult * (get(y))
#  )
#  # add arrows
#  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, #yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")
#  
#  #Add axis with perctentage
#  percentage <- round(diag(PC$Eval) / sum(PC$Eval) * 100, 2) #calculate percentage
#
#  
#  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
#  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, #arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")
#  
#  #ADD LABELS
#  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )
#  
#  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
#  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5,7.5,7.1,6)), y = #-(PCAloadings$PC2*c(4.3,2.6,5,7,5.8,6.5)+c(0,0,0,0,-0.15,0)),
#                          label = PCAloadings$Variables, color="black",size=3)
#  
#  #CHANGE THEME
#  #CHANGE THEME
#  
#  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)") 
#  
#  plot
#  
#}
#
# #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")

  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),ncol=3,nrow=2,  align = "hv")

```

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.cap= "**Figure 3.** Fitted posterior estimates of the presence-absence of interaction (a, b and c) and number of visits (d, e and f) of the different pollinator guilds in relation to the main axes of plant reproductive trait variation (PC1, PC2 and PC3). PC1 represents the flower number - flower size axis, PC2 represents the autonomous selfing - floral display axis and PC3 represents the style length - autonomous selfing axis. For visualization purposes due to large differences between number of visits from bees and the rest of the pollinator guilds, the number of visits was log-transformed (Y-axis of lower panel)."}

#LOAD LIBRARIES 
#library(phytools)
#library(ape) #for phylogenetic distance
#library(dplyr) #data processing
#library(rtrees) #for phylogenetic distancelibrary(MASS)
#library(reshape2)
library(viridis) #COLOUR GGPLOT
#library(MASS)
library(ggplot2)
library(broman) #crayon colours
#library(tidyverse)
library(patchwork) #panel of plots
#library(brms)
#library(cmdstanr)

#Load theme for publication

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(2, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75),face="bold"),
           plot.subtitle = element_text(face="bold",size=rel(2))
     ))
}

p1 <- readRDS("../Main_Figures/figure_3_1.rds")
p2 <- readRDS("../Main_Figures/figure_3_2.rds")
p3 <- readRDS("../Main_Figures/figure_3_3.rds")
pp1 <- readRDS("../Main_Figures/figure_3_4.rds")
pp2 <- readRDS("../Main_Figures/figure_3_5.rds")
pp3 <- readRDS("../Main_Figures/figure_3_6.rds")

library(patchwork)

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3  & theme(legend.position = "bottom") &  guides(color = guide_legend(override.aes = list(size=6.5), keywidth=1.8, keyheight=0.1,default.unit="inch"))

combined + plot_layout(guides = "collect",ncol = 3)
```
